---
title: "Workflow of Sugar R Package"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Workflow of Sugar R Package}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(sugar)
```

The following workflow should be considered for the web application's smooth set up and operation. 

# Package flow


- Set up Google Cloud Platform credentials as mentioned in "How to set up Google Cloud Platform credentials". Set aside the Client ID and Client secret for the app. 

- Create the app skeleton.


```{r}
create_app_skeleton()
```

An R Shiny app skeleton with the following structure is created. 

```
├── ETCXXXX.Rproj
├── app
│   ├── server
│   │   ├── view_as_student.R
│   │   ├── student_server.R
│   │   └── staff_server.R
│   ├── www
│   │   ├── blc.png
│   ├── userinput.R
│   ├── tabs.R
│   ├── app.R
│   ├── Global.R
│   └── googlesheets.R

```
- Set unit information 

```{r}
unit_details<- unit_info(unit = "ETC5521", 
                         name = "Exploratory Data Analysis",
                         semester=1,year=2020,
                         lecturer = c("Emi Tanaka" = "emi.tanaka@monash.edu",
                         "Di Cook" = "dicook@monash.edu"))
```

- Set the app setup info such as details on app maintainer, client id and secret. 

```{r}

 setup_info <- setup_info(unit_details,
              client_id="xxxxxxx.apps.googleusercontent.com",
              client_secret="xxxxxx-xxxxxx",
              maintainer="xxxxx@.monash.edu")
```

- Initialize authentication for creating Google Sheets for storing information on students with their attendance and grades as well as authorized staff members. 

```{r}
initiate_auth(setup_info)
```


- Add the unit timetable and assessment information 

The information on the schedule and assessment should be in a dataframe as per the format below with the same column names and data types. 


```{r, echo=TRUE,eval=FALSE}
schedule <- readr::read_csv("schedule.csv")

```


```{r schedule, echo=FALSE, message=FALSE, warnings=FALSE, results='asis'}
tabl <- " 
| Class         | StartDate     | EndDate     |
| <chr>         | <date>        | <date>      |
|---------------|:-------------:|------------:|
| Lecture A     | 2021-09-20    | 2021-12-10  |
| Lecture B     | 2021-09-21    | 2021-12-11  |
| Tutorial A    | 2021-09-22    | 2021-12-12  |
| Tutorial B    | 2021-09-23    | 2021-12-13  |
"
cat(tabl)
```

```{r  echo=TRUE,eval=FALSE}
assessment <- readr::read_csv("assessment.csv")
```

```{r assessment, echo=FALSE, message=FALSE, warnings=FALSE, results='asis'}
tab2 <- " 
| Assessment    | Weightage     | Total Marks  |
| <chr>         | <dbl>         | <dbl>        |
|---------------|:------------ :|------------: |
| ASSESS 1      | 25            | 100          |
| ASSESS 2      | 25            | 100          |
| ASSESS 3      | 25            | 100          |
| ASSESS 4      | 25            | 100          |
"
cat(tab2)
```

- Create Google Sheets for the unit

  + Attendance sheet : Google sheet for storing attendance of student.


```{r}
create_attendance_sheet(unit_details,schedule)
```

  + Grade sheet : Google sheet for storing attendance of student.
  
```{r}
create_grade_sheet(unit_details,assessment)
```

  + Student sheet : Google sheet for storing information on student such as name and Email Id.

```{r}
create_student_sheet(unit_details)
```

  + Authorization sheet : Google sheet for storing name and monash email id of authorized staff members. Only authorized individuals can access the app. 
  
```{r}
create_authorization_sheet(unit_details)
```

For ensuring uniqueness of the sheets,a unique id is created for the unit with its code, the semester period and the year. For example , `ETC5521S12020Attendance` denotes Attendance sheet for ETC5521 of Semester 1 of year 2020. For smooth functioning of the app, please ensure that the column names of the google sheets are unchanged. 


- Set up the user specific input such as unit code, client id and secret for the app

```{r}
user_input(setup_info)
```

The function writes the user specific input onto the `userinput.R` file for the functioning of the app.

- Launch the app

```{r}
launch_app()
```

You can get the google spreadsheet links using the code below if needed. 

```{r}
get_spreadsheet_links()
```

- Host the app on Monash EBS Shinyapps.io

Contact Emi Tanaka to get the application maintainer's email added to use the Monash EBS shiny account.
