---
title: "Workflow of Sugar R Package"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Workflow of Sugar R Package}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  eval = FALSE,
  comment = "#>"
)
```

```{r setup}
library(sugar)
```

The following workflow should be considered for the web application's smooth set up and operation. 

# Package flow


- Set up Google Cloud Platform credentials as mentioned in "How to set up Google Cloud Platform credentials". Set aside the Client ID and Client secret for the app. 

- Create the app skeleton.


```{r}
create_app_skeleton()
```

An R Shiny app skeleton with the following structure is created. 

```
├── ETCXXXX.Rproj
├── app
│   ├── server
│   │   ├── view_as_student.R
│   │   ├── student_server.R
│   │   └── staff_server.R
│   ├── www
│   │   ├── blc.png
│   ├── userinput.R
│   ├── tabs.R
│   ├── app.R
│   ├── Global.R
│   └── googlesheets.R

```
- Set unit information 

```{r}
unit_details<- unit_info(unit = "ETC5521", 
                         name = "Exploratory Data Analysis",
                         semester=1,year=2020,
                         lecturer = c("Emi Tanaka" = "emi.tanaka@monash.edu",
                         "Di Cook" = "dicook@monash.edu"))
```

- Set the app setup info such as details on app maintainer, client id and secret. 

```{r}

 setup_info <- setup_info(unit_details,
              client_id="xxxxxxx.apps.googleusercontent.com",
              client_secret="xxxxxx-xxxxxx",
              maintainer="xxxxx@.monash.edu")
```

- Initialize authentication for creating Google Sheets for storing information on students with their attendance and grades as well as authorized staff members. 

```{r}
initiate_auth(setup_info)
```


- Add the unit timetable and assessment information 

The information on the schedule and assessment should be in a dataframe as per the format below with the same column names and data types.

  + Column names of schedule : "Class","StartDate","EndDate"
  
  + Column names of assessment : "Assessment","Weightage","Total Marks"



```{r, echo=TRUE,eval=FALSE}
schedule <- readr::read_csv("schedule.csv")


```


```{r schedule, echo=FALSE,eval=TRUE, message=FALSE, warnings=FALSE}
data.frame("Class"=c("Lecture A","Lecture B", "Tutorial A"),
       "StartDate"=c(as.Date("20-09-2021", format = "%d-%m-%Y"),
                     as.Date("21-09-2021", format = "%d-%m-%Y"),
                     as.Date("22-09-2021", format = "%d-%m-%Y")),
       
       "EndDate"=c(as.Date("10-12-2021", format = "%d-%m-%Y"),
                     as.Date("11-12-2021", format = "%d-%m-%Y"),
                     as.Date("12-12-2021", format = "%d-%m-%Y")))
```

```{r  echo=TRUE,eval=FALSE}
assessment <- readr::read_csv("assessment.csv")
```

```{r assessment,eval=TRUE, echo=FALSE, message=FALSE, warnings=FALSE}

data.frame("Assessment"=c("ASSESS 1","ASSESS 2", "ASSESS 3","ASSESS 4"),
       "Weightage"=25,
       
       "Total Marks"=100)
```

- Create Google Sheets for the unit

  + Attendance sheet : Google sheet for storing attendance of student.


```{r}
create_attendance_sheet(unit_details,schedule)
```

  + Grade sheet : Google sheet for storing attendance of student.
  
```{r}
create_grade_sheet(unit_details,assessment)
```

  + Student sheet : Google sheet for storing information on student such as name and Email Id.

```{r}
create_student_sheet(unit_details)
```

  + Authorization sheet : Google sheet for storing name and monash email id of authorized staff members. Only authorized individuals can access the app. 
  
```{r}
create_authorization_sheet(unit_details)
```

For ensuring uniqueness of the sheets,a unique id is created for the unit with its code, the semester period and the year. For example , `ETC5521S12020Attendance` denotes Attendance sheet for ETC5521 of Semester 1 of year 2020. For smooth functioning of the app, please ensure that the column names of the google sheets are unchanged. 


- Set up the user specific input such as unit code, client id and secret for the app

```{r}
user_input(setup_info)
```

The function writes the user specific input onto the `userinput.R` file for the functioning of the app.

- Launch the app

```{r}
launch_app()
```

You can get the google spreadsheet links using the code below if needed. 

```{r}
get_spreadsheet_links()
```

- Host the app on Monash EBS Shinyapps.io

Contact Emi Tanaka to get the application maintainer's email added to use the Monash EBS shiny account.

For the log out from the app to be smooth, the shinyapps.io link should be supplied in the `app.R` file at the end. Replace the link "https://ebsmonash.shinyapps.io/sugar-demo-app/" with the newly created one. 
